\documentclass[twocolumn]{article}
\input{preamble.tex}

\begin{document}
\input{sections/summary}
\title{Evening the Odds:\\ The Impact of Town-Opposed Roles in Social Deduction 
Games\\ \small An experimental analysis of the impact of various 
town-opposed roles in social deduction games, using epistemology}
\author{
	Hugin Juliansson Zachariasen \\ Aalborg University \\ hjulia21@student.aau.dk
	\and
	Kristian Hadberg Mikkelsen \\ Aalborg University \\ khmi22@student.aau.dk
	\and
	Lucas Mørk Frendorf \\ Aalborg University \\ lfrend21@student.aau.dk
	\and
	Nicklas Peter Kvist Gislinge \\ Aalborg University \\ ngisli21@student.aau.dk
}
\maketitle
\begin{abstract}
%Original
	For this paper, we seek out to try and solve the win rate issues some social deduction games have. This winrate issue happens when the larger team, introduces many extra roles with speical powers. For this we moddeled our own social deduction game, based on the online game Town of Salem. We utilize epistemic dynamic inquery language  to moddel the knowlegde that our agenst base their actions on. Through our research, we have concluded that, for the small and informed team, getting more information and being able to consistenly remove a player from the larger team is what has proved the most beneficial.

%ChatGPT
In this paper, we address the win rate issues that arise in some social deduction games when larger teams introduce numerous extra roles with special powers. To investigate this, we modeled our own social deduction game based on the online game Town of Salem. We utilized epistemic dynamic inquiry language to model the knowledge that our agents base their actions on. Our research concluded that for the smaller, informed team, obtaining more information and consistently removing players from the larger team proved to be the most beneficial strategy.
\end{abstract}

\input{sections/introduction}
\input{sections/related-works.tex}
\input{sections/modeling.tex}
\input{sections/terminology.tex}
\input{sections/implementation.tex}
\input{sections/results.tex}
\input{sections/discussion.tex}
\input{sections/conclusion.tex}
\input{sections/future-works.tex}
\clearpage
\appendix
\makeatletter
\def\@seccntformat#1{\appendixname\ \csname the#1\endcsname: }
\makeatother

\input{sections/appendixA.tex}
\input{sections/appendixB.tex}

\clearpage
% Bibliography
\printbibliography[heading=bibintoc, title=Bibliography]
\label{bib:mybiblio}

\end{document}
