\section{Appendix A}\label{app:A}
The following is a detailed description of the different roles and their unique nightly actions: \\
\textbf{Roles allied to the town:} 
\begin{enumerate}
	\item\textbf{Villager} is a  role with no special actions. Typically given to the majority of the town. 
	\item\textbf{Sheriff} must choose one player each night and privately gain information regarding their faction. 
	\item\textbf{Investigator} must choose one player each night and privately gain information regarding a selection of roles that that player may have, one of them being true.
	\item\textbf{Doctor} must choose one player each night and protect them from any harm that may come to them during the night. 
	\item\textbf{Escort} must choose one player each night and prevent them from performing any actions during the night phase.
	\item\textbf{Veteran} may choose to go on alert during the night phase, if they do so, then anyone targeting them at night will die. 
	\item\textbf{Vigilante} may choose to kill any one player during the night phase, if that player is revealed to be a member of the town during the morning phase, the vigilante loses their killing ability, and will die the following morning.
\end{enumerate}
\textbf{Roles allied to the mafia:} 
\begin{enumerate}
	\item\textbf{Godfather} must choose one player each night who will die. 
	\item\textbf{Mafioso} performs the killing on the Godfathers behalf. If the Godfather is targeted by an escort, then the mafioso may independently choose who to kill. If the mafioso is targeted by the escort, then the Godfather kills their chosen target themselves.
	\item\textbf{Consigliere} must choose one player each night and privately gain information regarding their role. 
	\item\textbf{Consort} must choose one player each night and prevent them from performing any actions during the night phase.
	\item\textbf{Framer} must choose one player each night to frame. A framed player appears to be a member of the mafia if chosen by the Sheriff on this night.
	\item\textbf{Blackmailer} must choose one player each night to blackmail. A blackmailed player can only choose the “do not say anything” communicative action. 
\end{enumerate}