\section{Appendix A}\label{app:A}
\begin{center}
	\textbf{Game Roles}
\end{center}
The following is a detailed description of the different roles and their unique
nightly actions:

\textbf{Roles allied to the town:}
\begin{enumerate}
	\item\textbf{Villager (V)} is a  role with no special actions. Typically
	      given
	      to the majority of the town.
	\item\textbf{Sheriff (S)} must choose one player each night and privately
	      gain
	      information regarding their faction.
	\item\textbf{Investigator (I)} must choose one player each night and
	      privately
	      gain information regarding a selection of roles that that player may have,
	      one of them being true.
	\item\textbf{Doctor (D)} must choose one player each night and protect them
	      from any harm that may come to them during the night.
	\item\textbf{Escort (E)} must choose one player each night and prevent them
	      from performing any actions during the night phase.
	\item\textbf{Veteran (Ve)} may choose to go on alert during the night
	      phase, if
	      they do so, then anyone targeting them at night will die.
	\item\textbf{Vigilante (Vi)} may choose to kill any one player during the
	      night
	      phase, if that player is revealed to be a member of the town during the
	      morning phase, the vigilante loses their killing ability, and will die the
	      following morning.
\end{enumerate}
\textbf{Roles allied to the mafia:}
\begin{enumerate}
	\item\textbf{Godfather (G)} must choose one player each night who will die.
	\item\textbf{Mafioso (M)} performs the killing on the Godfathers behalf. If
	      the
	      Godfather is targeted by an escort, then the mafioso may independently
	      choose who to kill. If the mafioso is targeted by the escort, then the
	      Godfather kills their chosen target themselves.
	\item\textbf{Consigliere (Cg)} must choose one player each night and
	      privately
	      gain information regarding their role.
	\item\textbf{Consort (Ct)} must choose one player each night and prevent
	      them
	      from performing any actions during the night phase.
	\item\textbf{Framer (F)} must choose one player each night to frame. A
	      framed
	      player appears to be a member of the mafia if chosen by the Sheriff on this
	      night.
	\item\textbf{Blackmailer (B)} must choose one player each night to
	      blackmail. A
	      blackmailed player can only choose the “do not say anything” communicative
	      action.
\end{enumerate}