\section{Modeling}
As mentioned earlier, we wish to model a framework of games instead of one
specific one, in order to encapsulate as many parameters as possible. The game
that will be modeled will have two factions, henceforth known as the town and
mafia. The town wins when they have eliminated all mafia members, and the mafia
wins when their factions have the non-strict numerical majority of players. The
game is played out in rounds consisting of four phases, which happen in order,
until either win-condition is met: The night phase is where different roles
perform private or public actions to gain information or spread misinformation.
The morning phase is where public results of the night phase are revealed to
all players. The role of players who died during the night phase is revealed at
this time. The day phase is where players try to influence each other's
worldviews through communicative actions. The voting phase is where players
vote for who to lynch according to their individual worldviews. The voting
phase can end in a majority vote which will result in a lynching of that
player, killing them and revealing their role publicly, or in a tie, which will
result in the phase ending with no lynching. The possible roles that a player
can play in this modeling of the game, and their associated actions, are: Town
Roles: A Villager has no special actions. The Sheriff must choose one player
each night and privately gain information regarding their faction. The investigator must choose one
player each night and privately gain information regarding a selection of roles that that player
may have, one of them being true. The Doctor must choose one player each night
and protect them from any harm that may come to them during the night. The
Escort must choose one player each night and prevent them from performing any
actions during the night phase. The Veteran may choose to go on alert during
the night phase, if they do so, then anyone visiting them at night will die.
The Vigilante may choose to kill any one player during the night phase, if that
player is revealed to be a member of the town during the morning phase, the
vigilante loses their killing ability, and will die the following morning.
Mafia Roles: The Godfather must choose one player each night who will die. The
Mafioso performs the killing on the Godfathers behalf. The Framer must choose
one player each night to frame. A framed player appears to be a member of the
mafia if chosen by the Sheriff on this night. The Blackmailer must choose one
player each night to blackmail. A blackmailed player can only choose the “do
not say anything” communicative action.

Now, to simulate the games as closely as possible to the real world we use a 
foundation built upon a probabilistic approach to decision making, and an 
epistemological approach to the acquisition and refreshing of 
knowledge\cite{commitment}.
Their core principles are that players keep track of all possible worlds that
may be possible based on their own knowledge, and the public knowledge
available to them. They keep track of beliefs and lies by “marking” worlds
which contradict statements made by other players. Due to the fact that there
should always be more players belonging to the town than the mafia, and that
the players of the town have no reason to lie, it is presumed that the world
with fewest “marks” must be the true world, which the player will base their
decisions on. A few modifications to their methodology have been made, in order
to better suit a multi-round game. First, the communicative actions for the
game have been altered slightly. In this simulation, players can choose between
6 different communicative actions:

\begin{enumerate}
    \item Claim to have a certain role.
    \item Claim that someone else has a certain role.
    \item Claim to have performed a nightly actions, with some result.
    \item Inquire another player regarding their role.
    \item Inquire another player regarding their beliefs about other players.
    \item Do not say anything.
\end{enumerate}
The purpose of these actions are to mimic the in-person game as closely as
possible. Players will each be able to take 3 communicative actions before the
phase concludes. Players choose which actions to take, based on which action
will influence others’ most towards their own world view. If multiple actions
are in accordance with their world view, then they may choose to inquire other
players in order to maximize their information gain. When public information is
revealed, like the role of a killed player, all players must update their
worldviews, eliminating all worlds not in accordance with this information.
This will slowly limit the possible worlds, granting more information to the
town. The marks generated by communicative actions are associated with the
player that generated it, meaning that whenever public information is revealed
about that player, villagers may either discard or reinforce said marks,
depending on whether the player was revealed to be a member of the mafia,
meaning that may have had incentive to lie, or if they were a villager, meaning
they should have only told the truth. Another thing, kept track of by the
players, are the active and inactive worlds. An active world is a world that is
true based on the public and private information available to a player. An
inactive world is a world that is true based on the public information
available, but false based on the private information available. The need for
inactive worlds, is that a player cannot assume that other players are aware of
private information, so these worlds must be included when deciding which
communicative actions to perform during the day phase. An example: Player 1 is
a seer, and has used their nightly action to look at the faction of player 2,
which gave them the private information that player 2's faction is of the town.
Player 1 can now mark all worlds where player 2 is part of the mafia as
inactive, as they are factually false, but since this is not public information
player 1 knows that not everyone knows this, and these worlds must therefore
still be considered when choosing communicative actions, even if just for
knowing which worlds to avoid promoting.
