\section{Related Works}
A sizable amount of research has been put into the field of social deduction 
games. However, much of that research has been focused on strategies relating 
to when and how to utilize different communicative actions\cite{commitment}. 
Others focus on ways for the town to detect the mafia 
members\cite{werewolf_stealth}, or protect key town members from the 
mafia\cite{werewolf_nash_equilibrium}, and others still focus on the different 
decision making strategies that can be implemented in multi agent systems, 
which these games can be modeled 
as\cite{modelling_multi_agent_epistemic_systems}\cite{multi_agent_epistemic_planner_common_knowledge}\cite{probibalistic_multiagent_systems}.
However, one thing that is noticeably absent from this research is analyses 
with the focus of "evening the odds" for the mafia team when faced with a town 
full of special roles. The outcome of such an analysis might be a game setup 
where everyone involved can have a role with special abilities, meaning that 
players will likely be more engaged and active, throughout all stages of the 
game. \\ \\
A paper authored by Eger and Martens\cite{commitment} analyzed the effect of 
commitment to a plan in the game One Night Ultimate Werewolf. They modeled this 
using Dynamic Epistemic Logic, allowing each agent to be aware of multiple 
different possible worlds with alternating sets of facts, and sorting them 
based on the least likelihood of it being true. This is achieved by ‘marking’ 
worlds with statements made by other agents if these worlds contained lies made 
by the other agents. When an agent needs to choose what to base their next 
action on, they determine that based on the number of marks of other players, or randomly, if they have no facts. They proclaim this gives the agents a certain degree of 
planning. However, due to the increasing amount of worlds generated by new 
actions performed, many of them equivalent, a notion of commitment is 
introduced, in which they will stick with a certain plan until another plan is 
valued significantly higher. They compare this commitment to a baseline of 
random actions by villagers, resulting in a high win percentage for werewolves, 
proving their hypothesis. In a game of both werewolves and villagers with 
weighted worlds, they found that simply valuing the plans equally, that is 
choose the new plan if it is at least as good as the previous, resulted in the 
lowest win percentage for werewolves. \\ \\
The Interrogative Model of Inquiry (IMI) 
and Dynamic Epistemic Logics (DEL) are both central paradigms of formal 
epistemology, but where one lacks, the other excels. While IMI provides 
knowledge reasoning and inference in a multi-turn information-gathering process 
between an Inquirer and Nature, DEL models how each agent updates their 
knowledge in a multi-agent setting. \\
In 2014 Y.Hamami\cite{delimi} published a 
formalization of how to combine these, which combines the information-gathering 
process in an inquiry with respect to multi-agent dimensions. As opposed to 
standard IMI or DEL, the proposed DELIMI sees information as acquired by either 
common knowledge or from other agents in an interrogation. The inclusion of 
agents also introduces the notion of lying, that is answering an interrogative 
question with non-factual information, closely representing the nature of 
social deduction games. In reality, both the intrigue and the complexity of 
social deduction games often arise from the discussions involved between 
players, which we see as a core part of this type of game. While other works 
related to social deduction games have resorted mostly to rely on simple 
one-way actions, the DELIMI model allows agents to interrogate others, perhaps 
challenge their claims, find inconsistencies, or use logical inference to 
establish presuppositions.

To formally describe the concepts related to the modeling of this simulation, 
we draw upon the foundational contributions of both Hintikka\cite{hintikka} and 
Baltag\cite{Baltag}. Additionally, there are multiple other sources which grant 
foundational knowledge and semantics for describing multi agent systems. Such 
sources are related to inquiry\cite{delimi}, modeling knowledge and 
information\cite{modelling_multi_agent_epistemic_systems}, planning with common 
knowledge\cite{multi_agent_epistemic_planner_common_knowledge}, and 
probabilistic approaches\cite{probibalistic_multiagent_systems}. 
All of these were instrumental in the pursuit of knowledge regarding this area 
of research, and in building an adequate vocabulary to describe actions, 
belief, knowledge, and epistemology in general. 