\onecolumn
\begin{center}
	\section*{Summary}\label{sec:summary}
\end{center}
This paper investigates the disparity between win-rates of opposing teams in
social deduction games with an abundance of special roles. To do  this, an
approach based on epistemic logic and common sense is used to create a
simulation that emulates physical games of this type. The formalization of the
game is based on similar approaches within the same field, combining previous works based on dynamic epistemology with inquiry epistemology,
which we hypothesize to more realistically reflect the actual game. This formalization allows agents to model the anticipated answer to any question, and then build goal-oriented
paths of questions to other agents, from which they can deduce and infer facts or reveal lies. Additionally, agents are able to update their modelled view of worlds, based on newly acquired facts.
This combination of fields in epistemology lays the groundwork of inference in the simulation,
as well as providing a formal framework for the description of behaviour
reliant on logical formulae within the simulation. \\
The game that we have modelled is phase based. This means that in different phases, the players can make different actions. During the day phase, the players can communicate with each other, and share their beliefs and knowledge. In the night phase some players may take a nightly action. The players are divided into two factions. The town faction and the mafia. Further, each player is assigned a role based on which faction they are. Each role has a unique nightly action. As an example, the sheriff may look at another player, and see what faction they belong to. The sheriff is one of two investigative roles that belong to the town. The consigliere is the only investigative role, that belongs to the mafia. The consigliere may look at another player and reveal their exact role. In this game, all mafia member have knowledge of each other, and because of that, the nightly action and targeting preferences of the consigliere is different to the sheriff.
When a player has to decide who they are going to use their action on, we utilize the knowledge and beliefs they have gathered using our dynamic epistemic inquiry language. \\
The simulation was built with a truth-table approach, resulting in a heavy
computational burden, but with the benefit of being easy to understand
intuitively. \\
The simulation was run with a multitude of different team compositions. This
resulted in the revelation that the most important factor to consider, when
aiming for the creation of balanced social deduction games, is that killing-heavy mafia teams perform better than any other composition. Secondly, the ratio of mafia members to town members, is very impactful, but killing-heavy compositions may equalize this imbalance somewhat. Lastly, excluding killing-heavy teams showed that teams with the ability to acquire new information quickly performed better than those who could stop the town from performing their nightly actions.\\
The implementation is built upon .dotnet which includes object orientated code
structures which were highly useful for this project. The code is built upon
different parts connected together to form a fully working social deduction game simulation.
Such parts include communication being separately called each round where each player
evaluates its communicative options a chooses the best deemed action.
This is built upon the players own view of the game using possible
worlds. Each player has a list of all possible combinations of the game, altering these throughout the game, adding and removing marks. These marks are
created from claims made by other players and may be altered when knowledge is revealed
throughout the game. These Claims being either defend, inquire, or accuse. Defend is chosen when a player finds it most advantageous to defend themselves as they might
be in the spotlight to be mafia. Inquire simply inquires information from other
players. Accuse directly accuses a specific player of being a
specific role.
\twocolumn